---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lmkknn.metrics

<!-- badges: start -->
<!-- badges: end -->

The goal of lmkknn.metrics is to ...

## Installation

You can install the development version of lmkknn.metrics from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSCI-310/dsci-310-group-16-pkg.")
```

## Example Use Cases:

This is a basic example which shows you how to solve a common problem:

```{r example}
library(lmkknn.metrics)
## basic example code
```


```{r cars}

```


Here are some examples of use cases for the functions provided in lmkknn.metrics:

target_df: Selecting the target variable and additional columns from a dataframe.
create_recipe: Creating a recipe object for modeling based on the specified target variable and predictors.
get_list_item: Retrieving the nth element of a given list.
create_model_prediction: Creating a prediction model using a trained model fit and a test dataset.
str_collapse: Collapsing a string of arguments and joining them by '+'.

Functions
target_df()
create_recipe()
get_list_item()
create_model_prediction()
str_collapse()
For more information on how to use each function, see the package documentation.

Contributing
We appreciate contributions to the lmkknn.metrics package. Please refer to our Contributing document and Code of Conduct for more information.

License
The software provided in this project is offered under the MIT open source license. Refer to the license file for more information.


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
